---
title: "skripsi"
author: "chindy"
date: "2022-11-12"
output: html_document
---

## Active Library
```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(plyr)
library(gvlma)
library(car)
library(stats)
library(boot)
library(caret)
```

## Import Data
```{r}
data <- read_csv("C:/Users/micha/Downloads/archive/dataset_Facebook.csv")
head(data)
```

## Describe Data
```{r}
glimpse(data)
```

## Deskriptif Data
```{r}
summary(data)
```

## Check Missing Value
```{r}
colSums(is.na(data))
```

## Impute Missing Value
```{r}
data$like[which(is.na(data$like))] <- median(data$like,na.rm=T)
data$share[which(is.na(data$share))] <- median(data$share,na.rm=T)
data$Paid[which(is.na(data$Paid))] <- 0

#check missingvalue [2]
colSums(is.na(data))
```

## Select Variable Numeric
```{r}
data_num <- data %>% select_if(is.numeric) %>% select(-c(Category))
summary(data_num)
```

## Distribution Variable Numeric
```{r}
data_num %>% ggplot(aes(x=data_num$`Post Month`)) + xlab("") + ggtitle("Post Month") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8) 

data_num %>% ggplot(aes(x=data_num$`Post Weekday`)) + xlab("") + ggtitle("Post Weekday") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8) 

data_num %>% ggplot(aes(x=data_num$`Post Hour`)) + xlab("") + ggtitle("Post Hour") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8) 

data_num %>% ggplot(aes(x=data_num$`Lifetime Post Total Reach`)) + xlab("") + ggtitle("Lifetime Post Total Reach") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime Post Total Impressions`)) + xlab("") + ggtitle("Lifetime Post Total Impressions") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime Engaged Users`)) + xlab("") + ggtitle("Lifetime Engaged Users") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime Post Consumers`)) + xlab("") + ggtitle("Lifetime Post Consumers") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime Post Consumptions`)) + xlab("") + ggtitle("Lifetime Post Consumptions") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime Post Impressions by people who have liked your Page`)) + xlab("") + ggtitle("Lifetime Post Impressions by people who have liked your Page") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime Post reach by people who like your Page`)) + xlab("") + ggtitle("Lifetime Post reach by people who like your Page") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Lifetime People who have liked your Page and engaged with your post`)) + xlab("") + ggtitle("Lifetime People who have liked your Page and engaged with your post") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$comment)) + xlab("") + ggtitle("comment") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$like)) + xlab("") + ggtitle("like") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$share)) + xlab("") + ggtitle("share") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Total Interactions`)) + xlab("") + ggtitle("Total Interactions") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

data_num %>% ggplot(aes(x=data_num$`Page total likes`)) + xlab("") + ggtitle("Page total likes") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```

## Select Variable Categoric
```{r}
data_cat <- data %>% select_if(negate(is.numeric)) %>% add_column(Category = data$Category) %>%   add_column(Paid = data$Paid)

table(data_cat$Type)
table(data_cat$Category)
table(data_cat$Paid)
```

## Proportion Label Variable Categoric
```{r}
data_cat %>% ggplot(aes(x=data_cat$Paid)) + xlab("") + ggtitle("Paid") + geom_bar(fill="#69b3a2", color="#e9ecef")

data_cat %>% ggplot(aes(x=data_cat$Category)) + xlab("") + ggtitle("Category") + geom_bar(fill="#69b3a2", color="#e9ecef")

data_cat %>% ggplot(aes(x=data_cat$Type)) + xlab("") + ggtitle("Type") + geom_bar(fill="#69b3a2", color="#e9ecef")
```

## Outlier Assumption [Percentage]
```{r}
outlier <- function(x){
  length(which(x >  mean(x) + 3 * sd(x) | x < mean(x) - 3 * sd(x))  ) / length(x)
}

t(colwise(outlier)(data_num))
```

## Correlation Assumption
```{r}
data_num = data_num[,-17]
cordata = cor(data_num)
view(data.frame(round(cordata,2)))
#plot from python 
```

## Coef Correlation > 0.8 [Multicolinearity]
```{r}
multico <- which(abs(cordata)>0.8 & row(cordata)<col(cordata), arr.ind=TRUE)
high_cor <- matrix(colnames(cordata)[multico],ncol=2)
view(as.data.frame(high_cor))
```

## Delete variable which is include multicolinearity
```{r}
data <- data %>% select(!c(`Post Month`,`Lifetime Post Consumers`,`Lifetime Engaged Users`,like,share,comment))
head(data)
```

## Convert Categoric to Numeric
```{r}
data$Type <- as.numeric(as.factor(data$Type))
data$Category <- as.numeric(data$Category)
data$Paid <- as.numeric(data$Paid)
str(data)
```

## PCA
```{r}
datax = data[,-13]
datay = data[,13]

pca_fit <- princomp(datax, scores = TRUE)
sum <- summary(pca_fit)

#summary pca
sum

#data PCA with rows
view(as.data.frame(sum$scores))

#scree plot
plot(pca_fit,type = "l", main ="Scree plot for PCA")
```

## Eigen Values of PCA
```{r}
pca_var <- pca_fit$sdev^2
t(as.data.frame(round(pca_var,2)))
```

## Percent variance explained of PCA
```{r}
pca_cov <- pca_var/sum(pca_var)
t(as.data.frame(round(pca_cov,2)))
```

## Cummulative percent explained of PCA
```{r}
round(cumsum(pca_cov), 2)
```

## Summary
```{r}
get_eigenvalue(pca_fit)
```

## PCA Data
```{r}
pca_data <- data.frame(PC1=pca_fit$scores[,1],
                       PC2=pca_fit$scores[,2],
                       Y = datay$`Total Interactions`)
#display data
view(pca_data)

#plot PC1 and PC2
#plot(pca_fit$scores[,1], pca_fit$scores[,2], xlab="PC1", ylab = "PC2",main = "Plot PCA")
```

## Contibute Variable in PCA
```{r}
pca.var = get_pca_var(pca_fit)
round((contrib = pca.var$contrib)[,c("Dim.1","Dim.2")],2)
```

```{r}
#cex.before <- par("cex")
#par(cex = 0.7)
#biplot(pca_fit)
```

## PC Distribution
```{r}
pca_data %>% ggplot(aes(x=pca_data$PC1)) + xlab("") + ggtitle("PC 1") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

pca_data %>% ggplot(aes(x=pca_data$PC2)) + xlab("") + ggtitle("PC 2") + geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

#Summary = distribution nonparametrics 
```

## Linearity Assumption use PCA DATA
```{r}
pca_regression = lm(pca_data$Y~.,data=pca_data)
pvalue <- round(summary(pca_regression)$coefficient,3)
view(as.data.frame(pvalue))

#Pvalue > 0.05 [Not Signficant]
#Summary = PC1 & PC2 Significant
```

## Find estimated coefficient
```{r}
coef_function <- function(formula, data, indices) {
  
  d <- data[indices,]             #allows boot to select sample
  fit <- lm(formula, data=d)      #fit regression model
  return(coef(fit))               #return coefficient estimates of model

  }

#perform bootstrapping with 50,100,150,200 replications
boot_50 <- boot(data=pca_data, statistic=coef_function, R=50, formula=pca_data$Y~PC1+PC2)
boot_100 <- boot(data=pca_data, statistic=coef_function, R=100, formula=pca_data$Y~PC1+PC2)
boot_150 <- boot(data=pca_data, statistic=coef_function, R=150, formula=pca_data$Y~PC1+PC2)
boot_200 <- boot(data=pca_data, statistic=coef_function, R=200, formula=pca_data$Y~PC1+PC2)
```

```{r}
pca_regression
```

## Bootstrap Replicate 50
```{r}
plot(boot_50, index=1) #intercept of model
plot(boot_50, index=2) #PC1 predictor variable
plot(boot_50, index=3) #PC2 predictor variable

#Rataan
colMeans(boot_50$t)-boot_50$t0

#standart deviation
apply(boot_50$t,2,sd)
```

## Bootstrap Replicate 100
```{r}
plot(boot_100, index=1) #intercept of model
plot(boot_100, index=2) #PC1 predictor variable
plot(boot_100, index=3) #PC2 predictor variable

#Rataan
colMeans(boot_100$t)-boot_100$t0

#standart deviation
apply(boot_100$t,2,sd)
```

## Bootstrap Replicate 150
```{r}
plot(boot_150, index=1) #intercept of model
plot(boot_150, index=2) #PC1 predictor variable
plot(boot_150, index=3) #PC2 predictor variable

#Rataan
colMeans(boot_150$t)-boot_150$t0

#standart deviation
apply(boot_150$t,2,sd)
```

## Bootstrap Replicate 200
```{r}
plot(boot_200, index=1) #intercept of model
plot(boot_200, index=2) #PC1 predictor variable
plot(boot_200, index=3) #PC2 predictor variable

#Rataan
colMeans(boot_200$t)-boot_200$t0

#standart deviation
apply(boot_200$t,2,sd)
```
## Percentile
```{r}
boot.ci(boot_50, type = "perc")
boot.ci(boot_100, type = "perc")
boot.ci(boot_150, type = "perc")
boot.ci(boot_200, type = "perc")
```
## BCA
```{r}

```

## Bootstrap bca, percentil
## Resampling 50,100,200